Replication of Gantman et al. 2024

### 2024-03-18 manuscript.qmd
update based on Jan's comments

@@

excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects)

@@

`r n_subjects` subjects participated in the study. After applying the exclusion criteria, `r n_subjects_remaining` subjects remain. `r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.

@@

We found a pop-out effect for both moral and fashion words. In the moral condition, participants were `r mean_moral_in_category`% accurate for moral words and `r mean_moral_out_category`% accurate for non-moral words. This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se %>% round(3)`, *z* = `r z_moral_pop_out %>% round(3)`, *p* = `r p_moral_pop_out %>% format(scientific=FALSE)`.

@@

eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdc") %>%
  filter(!subject %in% excluded_subjects) %>%
  filter(subject != "34") # really few usable segments
```

```{r}
#| label: Flip subject 01s responses
#| include: false

@@

```{r}
#| label: fig-grand-averages
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Grand average waveforms. Shaded areas represent +/- 1 SE.
#| echo: false

ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  scale_color_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_fill_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_linetype_manual(name="Word Category", labels=c("Moral/Fashion", "Non-Moral/Non-Fashion"), values=c("solid", "dashed"))+
  facet_grid(electrode~category, labeller=as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words", "Cz"="Cz", "Pz"="Pz" )))+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal(base_size=12)+
  theme(panel.grid = element_blank())
```

>>>>

```{r}
#| label: Exclude very poor EEG recordings
#| include: false

exclude_for_eeg_quality <- c("34")
```

@@

excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects, exclude_for_eeg_quality)

@@

`r n_subjects` subjects participated in the study. After applying the exclusion criteria, `r n_subjects_remaining` subjects remain. `r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_eeg_quality)` subjects were excluded for having poor EEG recordings, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.

@@

We found a pop-out effect fashion words, but not moral words.

In the moral condition, participants were `r mean_moral_in_category`% accurate for moral words and `r mean_moral_out_category`% accurate for non-moral words. This difference was not statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se %>% round(3)`, *z* = `r z_moral_pop_out %>% round(3)`, *p* = `r p_moral_pop_out %>% format(scientific=FALSE)`.

@@

eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdc") %>%
  filter(!subject %in% excluded_subjects)
```

```{r}
#| label: Flip subject 01s, 1/2 36s responses
#| include: false

@@

```{r}
#| label: fig-grand-averages
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Grand average waveforms. Shaded areas represent +/- 1 SE. Dotted vertical lines represent the time windows of interest.
#| echo: false

ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_vline(xintercept = c(200, 250, 350, 600, 800), linetype="dotted", alpha=0.6)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  scale_color_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_fill_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_linetype_manual(name="Word Category", labels=c("Moral/Fashion", "Non-Moral/Non-Fashion"), values=c("solid", "dashed"))+
  facet_grid(electrode~category, labeller=as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words", "Cz"="Cz", "Pz"="Pz" )))+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal(base_size=12)+
  theme(panel.grid = element_blank())
```
